Fermi and eROSITA bubbles

### 2021-10-27 paper.tex
update

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item Numerical features:
    \begin{enumerate}
      \item GPU acceleration with \textsc{gamer-sr} code.
      \item Special relativistic hydrodynamics.
      \item Using a new algorithm \citep{tseng2021} dedicated to the conversion between\
            primitive and conserved variable, significantly reducing\
            numerical error caused by catastrophic cancellation occurs frequently\
            within the jet-ISM interaction zones.
    \end{enumerate}
  \item Assumptions on cosmic-ray:
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have ignored the $\mathbf{B}$ field within\
            the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            We also assumed the magnetic field is highly entangled in small-scale (how small?), resulting in\
            the negligible cosmic-ray diffusion.
    \end{enumerate}
  \item Assumptions on gravity:
    \begin{enumerate}
      \item We have assumed relativistic gravity is insignificant.
      \item The ISM disk and atmosphere are subjected to the fixed external potential\
            contributed by disk bulge and dark matter halo.
      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
      \item We ignore the Milky Way rotation.
      \item We use the potential of isothermal slab to mimic the fixed gravitational potential of the stellar bulge.
      \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using\
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

>>>>

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item Numerical features:
    \begin{enumerate}
      \item GPU acceleration with \textsc{gamer-sr} code.
      \item Special relativistic hydrodynamics.
      \item We use a new algorithm \citep{tseng2021}, dedicated to the conversion between\
            primitive and conserved variables, to significantly reduce\
            numerical error caused by catastrophic cancellations that commonly occur\
            within the jet-ISM interaction zones.
    \end{enumerate}
  \item Assumptions on cosmic-ray:
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have ignored the $\mathbf{B}$ field within\
            the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            We also assumed the magnetic field is highly entangled in small-scale (how small?), resulting in\
            the negligible cosmic-ray diffusion.
    \end{enumerate}
  \item Assumptions on gravity:
    \begin{enumerate}
      \item We have assumed relativistic gravity is insignificant.
      \item The ISM disk and atmosphere are subjected to the fixed external potential\
            due to a disk bulge and dark matter halo.
      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
      \item We ignore the centrifugal force due to the rotation of Milky Way.
      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
      \item The interface between cold ISM disk and atmosphere is parallel to galactic plane and is pressure balanced.
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using\
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.
